\chapter*{Acknowledgements}

This dissertation is a milestone in my academic career. I have been fortunate learn theories and concepts which would have been impossible if I had not extensively carried out the needed research. I am grateful to a number of people who have guided and supported me throughout the research process and provided assistance for my venture, both technically and emotionally.

I would like to divide these acknowledgements in two parts: firstly, I would like to mention those who helped me, directly or indirectly, in terms of technical assistance and knowledge, expertise, advices and guidance during the development of this dissertation. And the other part is related to those who guided me and made never give up and maintaining focused until the end.

Beginning with the first part, and the most important person during the development of my dissertation, my supervisor, Pofessor Jorge Barbosa, who guided me in selecting the final theme for this research. My advisor was there throughout my preparation of the proposal and the conceptualization of its structure. I would not have been able to do the research and achieve learning in the same manner without his help and support. His recommendations and instructions have enabled me to assemble and finish the dissertation effectively. Additionally, He, also, gave me the opportunity to collaborate in \textit{Antarex} project, a n European project that «proposes a holistic approach capable of controlling all the decision layers in order to implement a self-adaptive application optimized for energy efficiency.»

I would also like to thank all the people from the laboratory where I performed my experiences and collaborated in Antarex's project, such as Professor João cardoso, João Bispo, Hamid Arabnejad, Tiago Carvalho, Luís Reis, Nuno Paulino, Ricardo Nobre and Pedro Pinto. They made my integration in this project much easier and helped me the best way they could and any time i asked.

A special thanks to Kremlin team, in the name of Saturnino Garcia, always ready to answer my questions and requests related to the Kremlin software.

For the second part, I would like to thank again my supervisor, Professor Jorge Barbosa, who accompanied me until the end of this process and did not allow me to give up, even in the most frustrating and dire moments.

I would also like to thank all my instructors and teachers, from the beginning of my education until the end of this fase, who throughout my educational career have supported and encouraged me to believe in my abilities. They have directed me through various situations, allowing me to reach this accomplishment.

Along side with my instructors and teacher, I would like to mention my friends from  my year's course: João Pereira, Henrique Ferrolho, João Soares, Maria Marques, José Paulo, Leonardo Faria, Pedro Castro, Rita Ferreira, Jorge Teixeira, Maria Miranda, José Cardoso, Sofia Reis, Pedro França, Gabriel Souto, David Azevedo, Pedro Faria, Vitor Teixeira and João Almeida, Sara Reis, who accompained me through this five years in university and without them it would a lot harder. The lessons learned, good and bad moments are a part of me, like this dissertation.

I would also like to specially thank more friends from my course, such as Simão Felgueiras, Francisca Paupério, Vitor Esteves, João Leal, Daniel Nunes, Cristiano Seabra,  Gonçalo Moreno, Filipe Reis, Eduarda Cunha, Daniela João, Carolina Azevedo, Mariana Silva, João Carvalho, Catarina Correia, Sofia Silva, António Ramadas, Sérgio Domingues,  Tiago Frutado, Diogo Vaz, Gustavo Silva, João Almeida, Beatriz Baldaia, Daniel Machado and João Monteiro, who, in some way, helped, guided, given me advices and lived with me during these five years in university.


I would like to mention mu friends form my birth place an elementary school who now-a-days I still make contact: Rik Rodrigues, Hugo Fernandes, Simão Teixiera, Rita Pinto, Rita Franco, Maria Silva, Catarina Cadilha, Sara Carvalho, Daniela Peixoto, Tiago Cunha, João Novo, Francisca Painhas, Ana Teixeira, Windy Noro and Guilherme Polónia, who still mean a lot to me and are always present when I need.

A special thanks to Rui Castro and Nino Rocha who were always so comprehensive, supportive and helpful every time i needed.

Finally, my mother, Maria Bordalo Morais, my father, Alberto Morais, my brothers, André and Pedro Bordalo Morais, and my grandfather, Humberto Bordalo Xavier, I would like to thank them for all the support, advices and help during all times, specially during the development of this dissertation.

In the end, to all that had supported and helped me along the course of this dissertation by giving
encouragement and providing the moral and emotional support I needed to complete my thesis.
To them, I am eternally grateful

\vspace{10mm}
\flushleft{João Bordalo}
